Comparison of simulation to theory

### 2016-02-08 sims/compare-to-theory.Rmd
oh, wrong recomb distance

```{r sim_results}
if (!exists("simchunks.file")) { 
    simchunks.file <- "simulation_SIGMA1_Ninds25000_ndemes50_s0.1_tau100_run2016-01-11_simsums_chunks.Robj" 
}
load(simchunks.file)  # provides 'chunks'
get_simparams <- function (fname) {
    strings <- c( sigma="SIGMA", ninds="Ninds", ndemes="ndemes", s="s", tau="tau" )
    lapply( strings, function (x) { as.numeric(gsub(sprintf(".*[/_]%s([0-9.]+)_.*",x),"\\1",simchunks.file)) } )
}
sim.params <- get_simparams( simchunks.file )
# recombination distances, hard-coded
sim.rvals <- c(0,0.01,0.5)
# spatial locations of the demes
xx <- seq_len(sim.params$ndemes)-(sim.params$ndemes+1)/2
theory.params <- list( sigma=trueSigma(sim.params$sigma), s=sim.params$s, tau=sim.params$tau, 
       density=sim.params$ninds/sim.params$ndemes,
       width=sim.params$ndemes )
simchunks.file
unlist(theory.params)
```

>>>>

```{r sim_results}
if (!exists("simchunks.file")) { 
    simchunks.file <- "simulation_SIGMA1_Ninds25000_ndemes50_s0.1_tau100_run2016-01-11_simsums_chunks.Robj" 
}
load(simchunks.file)  # provides 'chunks'
get_simparams <- function (fname) {
    strings <- c( sigma="SIGMA", ninds="Ninds", ndemes="ndemes", s="s", tau="tau" )
    lapply( strings, function (x) { as.numeric(gsub(sprintf(".*[/_]%s([0-9.]+)_.*",x),"\\1",simchunks.file)) } )
}
sim.params <- get_simparams( simchunks.file )
# recombination distances, hard-coded
sim.rvals <- c(0,0.5-0.01,0.5)
# spatial locations of the demes
xx <- seq_len(sim.params$ndemes)-(sim.params$ndemes+1)/2
theory.params <- list( sigma=trueSigma(sim.params$sigma), s=sim.params$s, tau=sim.params$tau, 
       density=sim.params$ninds/sim.params$ndemes,
       width=sim.params$ndemes )
simchunks.file
unlist(theory.params)
```
